---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
[![Test coverage](https://github.com/JinxuanBian/bis620.2022/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/JinxuanBian/bis620.2022/actions/workflows/test-coverage.yaml)
[![lint](https://github.com/JinxuanBian/bis620.2022/actions/workflows/lint.yaml/badge.svg)](https://github.com/JinxuanBian/bis620.2022/actions/workflows/lint.yaml)
[![R-CMD-check](https://github.com/JinxuanBian/bis620.2022/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JinxuanBian/bis620.2022/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

bis620.2022 is a package to plot the time-series data, with basic plot functions and spectral signature calculation as data process. It would be shown with UKBiobank accelerometry data.

It could be used for data containing columns named `time` or `freq` and other numeric variable.

Refer to the example data `ukb_accel` for more details.

### build situation overview:
[test coverage page](https://github.com/JinxuanBian/bis620.2022/blob/main/.github/workflows/test-coverage.yaml)

[lint results](https://github.com/JinxuanBian/bis620.2022/blob/main/.github/workflows/lint.yaml)

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/JinxuanBian/bis620.2022) with:
``` r
# install.packages("devtools")
devtools::install_github("JinxuanBian/bis620.2022")
```

## Example

This is a basic example which shows you how to solve a common problem:
```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
```

```{r example}
library(bis620.2022)
# call of UKBiobank accelerometry data
data(ukb_accel)
# plots UKBiobank accelerometry data
ukb_accel[1:1000, ] |> accel_plot()
# calculate spectral signature by taking the modulus of the
# Fourier coefficients of the signal
ukb_accel[1:1000, ] |>
  spectral_signature(take_log = FALSE) |>
  accel_plot()
```
