---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2022

<!-- badges: start -->
[![Test coverage](https://github.com/JinxuanBian/bis620.2022/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/JinxuanBian/bis620.2022/actions/workflows/test-coverage.yaml)
[![lint](https://github.com/JinxuanBian/bis620.2022/actions/workflows/lint.yaml/badge.svg)](https://github.com/JinxuanBian/bis620.2022/actions/workflows/lint.yaml)
[![R-CMD-check](https://github.com/JinxuanBian/bis620.2022/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JinxuanBian/bis620.2022/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

bis620.2022 is a package to examine how would the supplements of Vitamin D or Omega-3 affect the person-year of various types of cancers and cardiovascular, for which person-year is defined as the estimate of the actual time at risk. Additionally, how factors such as BMI and smoking would act in the given experimental trials are also considered.

Refer to the example data `vital` for more details.

## Installation

You can install the development version of bis620.2022 from [GitHub](https://github.com/JinxuanBian/bis620.2022) with:
``` r
# install.packages("devtools")
devtools::install_github("JinxuanBian/bis620.2022")
```

## Example

This is a basic example which shows you how to solve a common problem:
```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
```

```{r example}
library(bis620.2022)
# call of vital data
data(ukb_accel)
# plots the histogram of the time at risk of four groups, taking breast cancer as an example
vital_hist(vital, "brca")
# plot the scatter plot of the time at risk versus bmi for four groups with the effect of smoking and model with linear regression with linear line and equation shown, taking breast cancer as an example
vital_model_smoke(vital, "brca")
# this is for without effect of smoking
vital_model_nosmoke(vital, "brca")
```
